Defending Against Web Application Attacks: Approaches, Challenges and Implications \newline\newline \small{\textbf{Response to Review Comments}}

### 2016-07-25 docs/comments/comments.tex
minor changes

{\bf Comment 1:} ``Τhe analysis on the accuracy and performance overhead is not reasonable. The paper presents metrics that were originally reported in other papers, which were evaluated under different assumptions and settings. Simply listing the numbers found in those papers in a table might be misleading. However, the reviewer acknowledges that it is very difficult to have access to those systems for a fair comparison, and agrees with the recommendation on improving the availability of the source code and dataset in future research."\\

@@

\noindent
{\bf Comment 2:} ``Similarly, {\sc xss} is introduced as an attack that has two forms, reflected and
persistent.  However, even though it's mentioned later on, how would DOM-based
{\sc xss} fit into this breakdown?  I don't believe it does (neatly), and am of the
view that it constitutes a third category since it can be performed on-demand
and purely client-side across frames without persistence, combining aspects of
both of the above categories."\\

>>>>

{\bf Comment 1:} ``The analysis on the accuracy
and performance overhead is not reasonable.
The paper presents metrics that were originally
reported in other papers,
which were evaluated under different
assumptions and settings.
Simply listing the numbers found in those papers
in a table might be misleading.
However,
the reviewer acknowledges that it is very
difficult to have access to those systems for a fair comparison,
and agrees with the recommendation on improving
the availability of the source code and dataset
in future research."\\

@@

\noindent
{\bf Comment 2:} ``Similarly, {\sc xss} is introduced
as an attack that has two forms,
reflected and persistent.
However,
even though it's mentioned later on,
how would {\sc dom}-based {\sc xss} fit into this breakdown?
I don't believe it does (neatly),
and am of the view that it constitutes a third
category since it can be performed on-demand
and purely client-side across frames without persistence,
combining aspects of both of the above categories."\\
